What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-11-26 Manuscript files/Manuscript.qmd
updates to figure embeddings

# Results
@fig-varimps-red displays the variable importance measures for the subject-level covariates as extracted from the reduced model. Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs. white) color indicating larger importance measures.

![Red VarImps](figures/RF_VarImps_red.png){#fig-varimps-red}

The random forest variable importances as extracted from the extended model are displayed in @gif-varimps-ext.

![Ext VarImps](figures/RF_VarImps_ext.png){#fig-varimps-ext}

Figures X-Y depict the more specific decision trees that were fitted to better understand how different subject level covariates contribute to the observed effect heterogeneity.

# Integration of Results
-Einordnung der Ergebnisse 
-Country in general important as seen in the reduced model 
-association with country for almost all IMCEs 
--> Trees: mostly UK vs Rest (then more specific associations)
--> Gender relevant for perc. gdp. milit & civ. killed UKR 
--> Left-Right-Relevant for perc. gdp econ

@@

-Vergleich mit factorHet 
- short description of factor het results

-Vergleich mit “normaler” Subgruppen Analyse

Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität

>>>>

# Results
@fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model. Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs. white) color indicating larger importance measures.

![Ext VarImps](figures/RF_VarImps_ext_v2.png){#fig-varimps-ext}

@image-panel depicts 4 decision trees that were fitted to better understand how different subject level covariates contribute to the observed effect heterogeneity. These exemplary decision trees were selected regarding content and interpretation and to highlight how single decision tress can be utilized for model interpretation.

```{r image-panel, echo=FALSE, fig.align='center'}
#| fig-cap: "Exemplary deicision trees for predicting IMCEs based on Covariates."
library(gridExtra)
library(grid)
library(png)

# Load the images from your laptop
img1 <- rasterGrob(png::readPNG("figures/DecTree_ext_Civ_killed_Ukr_16k.png"), interpolate = TRUE)
img2 <- rasterGrob(png::readPNG("figures/DecTree_ext_RUS_Sold_killed_100k.png"), interpolate = TRUE)
img3 <- rasterGrob(png::readPNG("figures/DecTree_ext_Risk_Nuke_Moderate.png"), interpolate = TRUE)
img4 <- rasterGrob(png::readPNG("figures/DecTree_ext_Territ_Cession_8perc.png"), interpolate = TRUE)

# Create subfigure captions
label1 <- textGrob("a) Ukrainian Civilians Killed (16k vs. 4k)", 
                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
label2 <- textGrob("b) Russian Soldiers killed (100k vs. 25k)", 
                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
label3 <- textGrob("c) Risk of Nuclear Strike (10% vs. 0%)", 
                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
label4 <- textGrob("d) Territorial Cession (2014 LoC (8%)) vs. None", 
                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))

# Combine images and captions
panel1 <- arrangeGrob(img1, top = label1)
panel2 <- arrangeGrob(img2, top = label2)
panel3 <- arrangeGrob(img3, top = label3)
panel4 <- arrangeGrob(img4, top = label4)

# Add a blank grob as a spacer
spacer <- textGrob("", gp = gpar(fontsize = 5))

# Arrange the panels in a 2x2 grid with space between rows
grid <- grid.arrange(
  arrangeGrob(panel1, panel2, ncol = 2),
  spacer, 
  arrangeGrob(panel3, panel4, ncol = 2),
  nrow = 3, heights = c(0.45, 0.1, 0.45) 
)

```

<!-- This is how it should work using quarto syntax but doesnt display captions properly and is weirdly centered -->
<!-- ::::{#fig-group_label layout-ncol=2 layout-nrow=2} -->

<!-- :::{#firstcol .column width="50%"} -->

<!-- ![test1](figures/DecTree_ext_Civ_killed_Ukr_16k.png){#fig-civ_UKR} -->

<!-- ![test2](figures/DecTree_ext_RUS_Sold_killed_100k.png){#fig-sold_RUS} -->
<!-- ::: -->

<!-- :::{#secondcol .column width="50%"} -->

<!-- ![test3](figures/DecTree_ext_Risk_Nuke_Moderate.png){#fig-nuke} -->
<!-- ![test4](figures/DecTree_ext_Territ_Cession_8perc.png){#fig-territ} -->
<!-- ::: -->

<!-- Exemplary Single Decision Tree Partitions for Predicting IMCEs -->
<!-- :::: -->

## Integration of Results
-Einordnung der Ergebnisse 
-Country in general important as seen in the reduced model 
-association with country for almost all IMCEs 
--> Trees: mostly UK vs Rest (then more specific associations)
--> Gender relevant for perc. gdp. milit & civ. killed UKR 
--> Left-Right-Relevant for perc. gdp econ

@@

<!-- -Vergleich mit factorHet eher raus -->
<!-- - short description of factor het results  -->

-Vergleich mit “normaler” Subgruppen Analyse --> aka vergleich mit deren paper

## Methodological Discussion
Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität
